The Etiology of Cybersecurity

### 2022-03-18 reports/cimss_2022/main-cut.tex
anonymize authors in cimss submission

\author{Michele Ambrosi\inst{1} \and
Francesco Beltramini\inst{1} \and Federico De Meo\inst{1} \and Olivero Nardi\inst{1} \and Mattia Pacchin\inst{1} \and Marco Rocchetto}

\authorrunning{M. Ambrosi et al.}

\institute{V-Research\\
Verona, Italy\\
\email{knowledgezero@v-research.it}}
\maketitle

@@

\subsection{Cybersecurity Risk Assessment}\label{sec:secra}
\begin{figure}[t]
	\centering
	\includegraphics[width=.5\columnwidth]{v-secra.pdf}
	\caption{Cybersecurity Risk Assessment Tool}
	\label{fig:secra}
\end{figure}
To test our hypothesis we implemented a tool-chain (open-source with
AGPLv3 license, available at \autocite{v-research2020cybersecurity}) for the
identification of weaknesses and the calculation of potential insecure
configurations. The engineering of the $\abftheory$-framework for CPS is summarized in the UML
Class diagram in Fig.~\ref{fig:secraclassdiagram} (in appendix). 
As in Fig.~\ref{fig:secra}, the cybersecurity risk assessment process
starts with the definition of the use cases and architectural requirements.  In our process, the specification is manually
translated into a UML design where:
\begin{itemize}
	\item a \emph{deployment diagram} describes the \emph{physical
		architecture}. Each agent is defined as an UML node with (physical)
		ports, and agent' ports are connected via UML information flow
		connectors, representing the physical channel.
	\item a \emph{functional architecture} is linked to each agent in the
		deployment diagram and is defined by an \emph{object diagram}.
		The object diagram is composed by instances of functional
		blocks, connected via information flow connectors.
	\item the connection between the two diagrams is implemented by
		``sockets'', functional blocks connected to a 
		physical port.
\end{itemize}

>>>>

\author{}

\authorrunning{}

\institute{}
\maketitle

@@

\subsection{Cybersecurity Risk Assessment}\label{sec:secra}
\begin{figure}[t]
	\centering
	\includegraphics[width=.5\columnwidth]{v-secra.pdf}
	\caption{Cybersecurity Risk Assessment Tool}
	\label{fig:secra}
\end{figure}
To test our hypothesis we implemented a tool-chain (open-source with
AGPLv3 license, available at \autocite{v-research2020cybersecurity-anonymous}) for the
identification of weaknesses and the calculation of potential insecure
configurations. The engineering of the $\abftheory$-framework for CPS is summarized in the UML
Class diagram in Fig.~\ref{fig:secraclassdiagram} (in appendix). 
As in Fig.~\ref{fig:secra}, the cybersecurity risk assessment process
starts with the definition of the use cases and architectural requirements.  In our process, the specification is manually
translated into a UML design where:
\begin{itemize}
	\item a \emph{deployment diagram} describes the \emph{physical
		architecture}. Each agent is defined as an UML node with (physical)
		ports, and agent' ports are connected via UML information flow
		connectors, representing the physical channel.
	\item a \emph{functional architecture} is linked to each agent in the
		deployment diagram and is defined by an \emph{object diagram}.
		The object diagram is composed by instances of functional
		blocks, connected via information flow connectors.
	\item the connection between the two diagrams is implemented by
		``sockets'', functional blocks connected to a 
		physical port.
\end{itemize}
